---
title: "SSC_Retrieval"
output: rmarkdown::github_document
author: "Ilan Valencius"
use: "For retrieving USGS suspended sediment concentration and discharge data along a river transect"
---

## Import Packages

```{r packages}
library(dataRetrieval)
library(sp)
library(sf)
library(maptools)
library(magrittr)
library(maps)
library(rgdal)
library(ggplot2)
library(usmap)
library(stringr)
library(dataRetrieval)
library(dplyr)
library(patchwork)
library(dams)
library(data.table)
library(nhdplusTools)
library(riverdist)
library(GISTools)
library(rgeos)
library(tidyr)
library(qpcR)
```

## Set up imports

-   00060: discharge, cubic feet per second
-   80154: Suspended sediment concentration, milligrams per liter
-   Dates should be in in YYYY-MM-DD format

```{r imports}
wd_root <- 'D:/valencig/Thesis/USGS_dataquery'
centerline_kml <- "D:/valencig/Thesis/Data/chattahoochee_shape/chattahoochee_centerline.kml"

# Location of dams saved as kml files in dam_read_dir
# dam_names <- paste0(c("Buford Dam",
#                       "Morgan Falls",
#                       "Langdale Dam",
#                       "Eagle and Phoenix Dam",
#                       "West Point Dam",
#                       "Riverview Dam",
#                       "Bartletts Ferry Dam",
#                       "Goat Rock Dam",
#                       "Oliver Dam",
#                       "North Highlands Dam",
#                       "Walter F. George Dam",
#                       "George W Andrew Lock and Dam",
#                       "Jim Woodruff Dam"), ".kml")
# dam_read_dir <- "D:/valencig/Thesis/Data/chattahoochee_shape/dams/"

# When you want station info
startDate <- "1990-01-01"
endDate <- "1995-01-01"

## Query parameters for station data ##

# Daily value parameters
dv_parameters <- c("00060")
# Water quality parameters
wq_parameters <- c("80154") #(SSC, mgL)
# for WQP portal, characteristic name is hardcoded in
# Stat Codes
statCd <- c("00003") # stat code: mean

## If using station numbers from file ##

# 8 digit station numbers of interest, column name must be 'site_no'
station_file <- "D:/valencig/Thesis/usgs_SSC/imports/station_numbers.csv"
usgs_prefix <- FALSE # do station numbers have 'USGS-' in title

## If getting station data from transect ##
upstream_distance_km <- 686

## Dam info ## 
use_dam_file <- TRUE # if set to false will autoquery data from NID website
dam_file <- 'D:/valencig/Thesis/usgs_SSC/imports/nation.csv'

## Predicted SSC from landsat ##
landsat_csv <- 'D:/valencig/Thesis/chattahoochee-dams/chattahoochee-dams-exports/SSC_pred.csv'

## Don't touch this code ##

# helper function -> pads a character string with leading 0s (for USGS codes)
pad0 <- function(x) {
  while (nchar(x) < 8) {
    x <- paste0("0", x)
  }
  return(x)
}

centerline <- as.data.frame(maptools::getKMLcoordinates(centerline_kml, 
                                                        ignoreAltitude = TRUE))
names(centerline) <- c('lon','lat')
# Convert centerline to sf for plotting
centerline_sf <- st_as_sf(centerline, coords=c("lon","lat")) %>% st_set_crs(4326)
```

## Plot centerline transect

-   **Must run this cell**

```{r transect}
plot_dam <- function(dam_name){
  dam <- as.data.frame(t(as.data.frame(maptools::getKMLcoordinates(paste0(dam_read_dir, dam_name),
                                                        ignoreAltitude = TRUE))))
  names(dam) <- c('lon','lat')
  dam_transform <- usmap_transform(dam)
  geom_point(data = dam_transform,
             aes(x = x, y = y),
             color = "green",
             shape=2)
}

centerline_transform <- usmap_transform(centerline)

# Create Dam Map
dam_map = plot_usmap(fill = "black", alpha = 0.5, color = "white", size = 1,
           include= c("GA","FL", "AL"), labels = TRUE) +
  labs(title = "Chattahooche Centerline", subtitle = "Buford Dam to Brothers River") +
  geom_path(data = centerline_transform,
            aes(x = x, y = y),
            color = "red",
            size = 1) +
  lapply(dam_names, plot_dam)

dam_map

# Save Map
ggsave(dam_map,
       filename = 'exports/rivertransect.png',
       width = 5, height = 8)

```

## Get station info and plot station locations (from file)

```{r station plot}
# Function to remove empty columns of query
rm_empty <- function(data){
  empty_columns <- colSums(is.na(data) | data == "") == nrow(data)
  return(data[, !empty_columns])
}
stations <- read.csv(station_file,colClasses=c("character")) # read as character to keep leading zeros
if (usgs_prefix) {
  # remove USGS-prefix
  station_nums <- unlist(strsplit(stations$site_no, split='-'))[c(FALSE, TRUE)]
} else {
  station_nums <- stations$site_no
}
station_nums <- unlist(lapply(station_nums, pad0))
station_data <- readNWISsite(station_nums)
station_data <- rm_empty(station_data)

# To export information on stations to csv
write.csv(station_data, "exports/valencius_chattahoochee_usgs_stations.csv", row.names=FALSE)

station_transform = usmap_transform(station_data, 
                                      input_names = c("dec_long_va", "dec_lat_va"))

station_map <- plot_usmap(fill = "black", alpha = 0.5, color = "white", size = 1, 
           include= c("GA","FL", "AL"), labels = TRUE) +
  labs(title = "USGS Station Locations") +
  geom_path(data = centerline_transform,
            aes(x = x, y = y),
            color = "red",
            size = 1) +
  geom_point(data = station_transform,
              aes(x = x, y = y),
              color = "yellow",
             shape=4)

station_map

# Save Map
# ggsave(station_map,
#        filename = 'exports/valencius_stationlocs.png',
#        width = 5, height = 8)
```

## Query each station (from file)

```{r station info}
## Get daily discharge data ##
dv <- readNWISdv(station_nums, dv_parameters, startDate, endDate, statCd = statCd)
dv_filtered <- data.frame(dv["site_no"], 
                          dv["Date"],
                          dv["X_00060_00003"]) # X_00060_00003 will need to change depending on your stat codes
## Get water quality data ##
wq <- readWQPqw(paste0("USGS-", station_nums), wq_parameters, startDate, endDate)

#stations <- read.table(station_file, header = TRUE, colClasses = "character")

## Get daily discharge data ##
names(dv_filtered) <- c("site_no", "date", "discharge")

# Strip 'USGS-' identifier from station numbers
wq["MonitoringLocationIdentifier"] <- lapply(list(wq[["MonitoringLocationIdentifier"]]), substring,
                                               first = 6)
wq_filtered <- data.frame(wq["MonitoringLocationIdentifier"],
                            wq["ActivityStartDate"],
                            wq["ResultMeasureValue"])
names(wq_filtered) <- c("site_no","date", "sscmgL")
## To export station data to csv ##
write.csv(dv_filtered, "exports/stations_from_file/valencius_discharge.csv", row.names=FALSE)
write.csv(wq_filtered, "exports/stations_from_file/valencius_ssc.csv", row.names=FALSE)
```

## Automatically extract SSC and Q from stations

-   **Note:** this may take a while

```{r load data}
## Run if you have previously saved data from {r get basin} ##
save_dir <- paste0(wd_root, '/variables/')
load(file=paste0(save_dir, 'riverdata.Rdata'))
load(file=paste0(save_dir, 'nwis_stations.Rdata'))
load(file=paste0(save_dir, 'wqp_stations.Rdata'))
load(file=paste0(save_dir, 'SSC_full.Rdata'))
load(file=paste0(save_dir, 'Q_full.Rdata'))
```

```{r station extract}
save_dir <- paste0(wd_root,'/variables/')
if(!dir.exists(save_dir)){
    dir.create(save_dir)
}
if(!dir.exists(paste0(wd_root,'/exports/'))){
    dir.create(pate0(wd_root,'/exports/'))
}
## Determine Watershed Geometries ##
summarize.nldi = function(input){
  data.frame(name = names(input), 
             class = sapply(input, class)[1], 
             row.names = NULL) %>% 
    mutate(feature_count = ifelse(class == "sf", sapply(input, nrow), 
                                  sapply(input, length)))
}
# Get last lat, long pair from centerline
start_loc <- tail(centerline, 1)
start_loc <- c(start_loc[[1]], start_loc[[2]]) 
riverdata <- findNLDI(location = start_loc,
              nav = c("UT", "UM"),
              find = c("nwis", "WQP","basin", "flowlines"),
              distance_km = upstream_distance_km)

summarize.nldi(riverdata)

## Merge Site Names ##
# get all WQP sites
mc_names <- paste0("USGS-",lapply(riverdata$UM_WQP$comid, pad0))
ut_names <- paste0("USGS-",lapply(riverdata$UT_WQP$comid, pad0))
# merge with nwis sites
mc_names <- unique(append(mc_names, riverdata$UM_nwissite$identifier))
ut_names <- unique(append(ut_names, riverdata$UT_nwissite$identifier))
# Remove mislablled sites outside of the watershed (remove from ut and mc)
mc_names <- mc_names[- match("USGS-02297310",mc_names)]
mc_names <- mc_names[- match("USGS-02297272",mc_names)]
mc_names <- mc_names[- match("USGS-03298550",mc_names)]
ut_names <- ut_names[- match("USGS-02297310",ut_names)]
ut_names <- ut_names[- match("USGS-02297272",ut_names)]
ut_names <- ut_names[- match("USGS-03298550",ut_names)]
ut_names <- ut_names[- match("USGS-02296750",ut_names)]

## Get Dicharge Data ##riverdata$UM_nwissite$identifier
Q_mc <- data.table(readNWISdv(gsub("USGS-", "", mc_names), 
                parameterCd = dv_parameters, 
                startDate = startDate,
                endDate = endDate) %>% renameNWISColumns())[,":=" (
                  site_no = paste0("USGS-", site_no),
                  date = Date,
                  flow = Flow,
                  portal = 'NWIS',
                  channel = 'MAIN STEM'
                )][,.(site_no, date, flow, portal, channel)]
Q_ut <- data.table(readNWISdv(gsub("USGS-", "", ut_names), 
                parameterCd = dv_parameters, 
                startDate = startDate,
                endDate = endDate) %>% renameNWISColumns())[,":=" (
                  site_no = paste0("USGS-", site_no),
                  date = Date,
                  flow = Flow,
                  portal = 'NWIS',
                  channel = 'TRIBUTARY'
                )][,.(site_no, date, flow, portal, channel)]

# Remove main channel sites from ut sites
Q_ut <- anti_join(Q_ut, Q_mc, by="site_no")

## Get SSC data ##
SSC_wqp_mc <- data.table(readWQPdata(siteNumbers=mc_names, 
                parameterCd = wq_parameters,
                startDate=startDate,
                endDate=endDate
                ))[,":=" (
                  site_no = MonitoringLocationIdentifier,
                  date = ActivityStartDate,
                  sscmgmL = ResultMeasureValue,
                  portal = 'WQP',
                  channel = 'MAIN STEM'
                )][,.(site_no, date, sscmgmL, portal, channel)]

SSC_wqp_ut <- data.table(readWQPdata(siteNumbers=ut_names, 
                parameterCd = wq_parameters,
                startDate = startDate,
                endDate = endDate
                ))[,":=" (
                  site_no = MonitoringLocationIdentifier,
                  date = ActivityStartDate,
                  sscmgmL = ResultMeasureValue,
                  portal = 'WQP',
                  channel = 'TRIBUTARY'
                )][,.(site_no, date, sscmgmL, portal, channel)]
# Remove main channel sites from ut sites
SSC_wqp_ut <- anti_join(SSC_wqp_ut, SSC_wqp_mc, by="site_no")

## Combine upper tributaries and main channel ##
Q_full <- rbind(Q_mc, Q_ut)
SSC_full <- rbind(SSC_wqp_mc, SSC_wqp_ut)

## Identify Stations of Interest ##
# NWIS sites
mc_nwis_names <- unique(Q_mc$site_no)
ut_nwis_names <- unique(Q_ut$site_no)

mc_nwis <- data.table(whatNWISsites(site=gsub("USGS-", "",mc_nwis_names)))[,":="(
    portal = "NWIS",
    site_no = paste0("USGS-", site_no),
    lat = dec_lat_va,
    lon = dec_long_va,
    channel="MAIN STEM"
  )][,.(portal, site_no, station_nm,site_tp_cd, lat, lon, channel)]
ut_nwis <- data.table(whatNWISsites(site=gsub("USGS-", "",ut_nwis_names)))[,":="(
    portal = "NWIS",
    site_no = paste0("USGS-", site_no),
    lat = dec_lat_va,
    lon = dec_long_va,
    channel="TRIBUTARY"
  )][,.(portal, site_no, station_nm,site_tp_cd, lat, lon, channel)]

# WQP sites
mc_wqp_names <- unique(SSC_wqp_mc$site_no)
ut_wqp_names <- unique(SSC_wqp_ut$site_no)

mc_wqp <- data.table(whatWQPsites(siteid=mc_wqp_names))[,":="(
    portal = "WQP",
    site_no = MonitoringLocationIdentifier,
    station_nm = MonitoringLocationName,
    site_code = MonitoringLocationTypeName,
    drainage_area_km2 = DrainageAreaMeasure.MeasureValue*(2.58999/1.00000073), # sq mi -> sq km
    lat = LatitudeMeasure,
    lon = LongitudeMeasure,
    elevation_m = VerticalMeasure.MeasureValue *0.3048, # ft -> m
    channel="MAIN STEM"
  )][,.(portal, site_no, station_nm, site_code, lat, lon, drainage_area_km2, elevation_m, channel)]

# Often the case where SSC not measures on tributaries

ut_wqp <- data.table(whatWQPsites(siteid=ut_wqp_names))[,":="(
    portal = "WQP",
    site_no = MonitoringLocationIdentifier,
    station_nm = MonitoringLocationName,
    site_code = MonitoringLocationTypeName,
    drainage_area_km2 = DrainageAreaMeasure.MeasureValue*(2.58999/1.00000073), # sq mi -> sq km
    lat = LatitudeMeasure,
    lon = LongitudeMeasure,
    elevation_m = VerticalMeasure.MeasureValue *0.3048, # ft -> m
    channel="TRIBUTARY"
  )][,.(portal, site_no, station_nm, site_code, lat, lon, drainage_area_km2, elevation_m, channel)]  



## Map gauge location to river distance ## 

S1 <- as(riverdata$UM_flowlines, 'Spatial')
# trace(line2network, edit=T) --> comment out following two lines
# suppressMessages(out <- removemicrosegs(out))
# suppressMessages(out <- removeduplicates(out))
nldi_proj4 <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84"
AKalbers <- "+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154
    +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +ellps=GRS80 +towgs84=0,0,0"
river_center <- line2network(S1, reproject=AKalbers)
# Apply projection to mc nwis sites then convert into meter projection
mc_nwis_spatial <- mc_nwis
mc_nwis_spatial$lat <- as.numeric(mc_nwis_spatial$lat)
mc_nwis_spatial$lon <- as.numeric(mc_nwis_spatial$lon)
coordinates(mc_nwis_spatial) <- ~lon + lat
proj4string(mc_nwis_spatial) <- '+init=epsg:4326'
mc_nwis_spatial <- spTransform(mc_nwis_spatial, CRS(AKalbers))
mc_nwis_spatial <- as.data.frame(mc_nwis_spatial)
nwis_riv <- xy2segvert(x=mc_nwis_spatial$lon, y=mc_nwis_spatial$lat, rivers=river_center)
# Do the same for mc wqp sites
mc_wqp_spatial <- mc_wqp
mc_wqp_spatial$lat <- as.numeric(mc_wqp_spatial$lat)
mc_wqp_spatial$lon <- as.numeric(mc_wqp_spatial$lon)
coordinates(mc_wqp_spatial) <- ~lon + lat
proj4string(mc_wqp_spatial) <- '+init=epsg:4326'
mc_wqp_spatial <- spTransform(mc_wqp_spatial, CRS(AKalbers))
mc_wqp_spatial <- as.data.frame(mc_wqp_spatial)
wqp_riv <- xy2segvert(x=mc_wqp_spatial$lon, y=mc_wqp_spatial$lat, rivers=river_center)

# Determine distance from start of channel for nwis sites
distances_nwis <- list()
for (i in 1:length(nwis_riv$vert)){
  # Distance to mouth of river
  dist_m <- riverdistance(startseg = nwis_riv$seg[i], startvert = nwis_riv$vert[i],
                            endvert = 1, endseg = 1, rivers=river_center)
  # Convert from degrees to km
  distances_nwis <- append(distances_nwis, upstream_distance_km-dist_m/1000)
}
nwis_riv$dist_downstream_km <- distances_nwis

# Determine distance from start of channel for wqp sites
distances_wqp <- list()
for (i in 1:length(wqp_riv$vert)){
  # Distance to mouth of river
  dist_m <- riverdistance(startseg = wqp_riv$seg[i], startvert = wqp_riv$vert[i],
                            endvert = 1, endseg = 1, rivers=river_center)
  # Convert from degrees to km
  distances_wqp <- append(distances_wqp, upstream_distance_km-dist_m/1000)
}
wqp_riv$dist_downstream_km <- distances_wqp

## Merge station info ##
mc_nwis$dist2river_m <- nwis_riv$snapdist
mc_nwis$dist_downstream_km <- nwis_riv$dist_downstream_km
mc_wqp$dist2river_m <- wqp_riv$snapdist
mc_wqp$dist_downstream_km <- wqp_riv$dist_downstream_km

nwis_stations <- rbind(mc_nwis, ut_nwis, fill=TRUE)
wqp_stations <- rbind(mc_wqp, ut_wqp, fill=TRUE)

## Map stationd distances to Q and SSC measurements ##
Q_full <- left_join(Q_full, nwis_stations)
SSC_full <- left_join(SSC_full, wqp_stations)

## Convert variable data tables to upper case ##
nwis_stations <- mutate_all(nwis_stations, toupper)
wqp_stations <- mutate_all(wqp_stations, toupper)
Q_full <- mutate_all(Q_full, toupper)
SSC_full <- mutate_all(SSC_full, toupper)

## Save variables to save time ##
save(riverdata, file=paste0(save_dir, 'riverdata.Rdata'))
save(nwis_stations, file=paste0(save_dir, 'nwis_stations.Rdata'))
save(wqp_stations, file=paste0(save_dir, 'wqp_stations.Rdata'))
save(SSC_full, file=paste0(save_dir, 'SSC_full.Rdata'))
save(Q_full, file=paste0(save_dir, 'Q_full.Rdata'))

## Export data to csv ##
write.csv(Q_full, paste0(wd_root,"/exports/stations_autoquery/discharge_full.csv"), row.names=FALSE)
write.csv(SSC_full, paste0(wd_root,"/exports/stations_autoquery/ssc_full.csv"), row.names=FALSE)
write.csv(nwis_stations, paste0(wd_root, '/exports/stations_autoquery/discharge_stations.csv'), row.names=FALSE)
write.csv(wqp_stations, paste0(wd_root, '/exports/stations_autoquery/ssc_stations.csv'), row.names=FALSE)
```

## Determine locations of all dams in the watershed

-   Dam data cane be queried automatically or downloaded in csv form from the NID Website [<https://nid.usace.army.mil/#/downloads>]
-   **Note:** If you download the nation.csv which contains all NID data, you must remove the first row which contains the last date the file was modified (R uses the first row as column names)

```{r dam query}
## If importing from file ##
if (use_dam_file) {
  nid_dams <- read.csv(dam_file)
} else {
  ## CURRENTLY NOT WORKING
  nid_dams <- get_nid()
}

# Remove entries which are missing lat, lon
nid_dams <- na.omit(nid_dams, cols=c('Longitude','Latitude'))
# Convert to sf object
nid_dams_sf <- st_as_sf(nid_dams, coords = c("Longitude", "Latitude")) %>% st_set_crs(4326)

# Get dams in the basin
basin_dams <- st_intersection(nid_dams_sf,riverdata$basin$geometry)
```

# Start Making Plots

## Compare Centerline KML and NLDI

```{r NLDI sanity check}
centerline_compare <-
ggplot() + 
  geom_sf(data = riverdata$basin) + 
  geom_sf(data = centerline_sf, col = "red", alpha = .5, size = 1)+
  theme_void() +
  labs(caption = "Input extent") +
ggplot() +
  geom_sf(data = riverdata$basin, col = NA) + 
  geom_sf(data = riverdata$UM_flowlines, col = "blue",size = 1) +
  theme_void() +
  labs(title = "Streamflow",
       caption = "NLDI extent") + 
  theme(legend.position = "none",
         plot.title = element_text(face = "bold", hjust = .5))

centerline_compare

# Save Map
ggsave(centerline_compare, 
       filename = 'exports/centerline_compare.png',
       width = 5, height = 8)
```

## Plot all NWIS stations (time independent)

```{r NWIS stations}
## Plot Station Data ##
nwis_stations <- ggplot() + 
  ## Basin and Channels ##
  geom_sf(data = riverdata$basin) + 
  geom_sf(data = riverdata$UM_flowlines, col = "blue") + 
  geom_sf(data = riverdata$UT_flowlines, col = "blue", alpha = .5, lwd=0.25) + 
  theme_bw() +
  coord_sf(label_graticule = 'NESW') +
  
  geom_sf(data = riverdata$UM_nwissite, shape = 21, 
          fill = NA, stroke = 0.75, size = 1.5, color="red") + # Shape aes: USGS gage, set with scale_shape_manual
  geom_sf(data = riverdata$UT_nwissite, shape = 21, 
          fill = NA, stroke = 0.25, size = 0.5, color="red") + # Shape aes: USGS gage, set with scale_shape_manual 
  scale_size_continuous(range = c(1,7)) +
  scale_color_brewer(palette = "Set1") +
  #theme_void() +
  labs(title = "USGS Station Locations") + 
  theme(legend.position = "none",
         plot.title = element_text(face = "bold", hjust = .5))

nwis_stations

# Save Map
ggsave(nwis_stations,
       filename = 'exports/usgs_stations.png',
       width = 5, height = 8)
```

## Plot locations of USGS stations which measure discharge (in time period)

```{r discharge stations}
## Plot Station Data ##
nwis_plot<-nwis_stations%>%st_as_sf(coords=c('lon','lat')) %>% st_set_crs(4326)
discharge_locs <- ggplot() + 
  ## Basin and Channels ##
  geom_sf(data = riverdata$basin, show.legend = F) + 
  geom_sf(data = riverdata$UM_flowlines, col = "blue", show.legend = F) + 
  geom_sf(data = riverdata$UT_flowlines, col = "blue", alpha = .5, lwd=0.25, show.legend = F) + 
  theme_bw() +
  scale_size_continuous(range = c(1,7)) +
  
  ## Upper main channel#
  geom_sf(data = nwis_plot, aes(color=channel, shape=channel, size=channel),  fill = NA, stroke = 0.75) + 
  #scale_size_continuous(range = c(1,7)) +
  #scale_color_brewer(palette = "Set1") +
  scale_color_manual(values = c('green', 'red')) +
  scale_shape_manual(values = c(21, 1)) +
  scale_size_manual(values = c(3, 1)) +
  #theme_void() +
  coord_sf(label_graticule = 'NESW') +
  labs(title = "USGS Station Locations Measuring Discharge",
       caption = paste0(startDate, ' to ', endDate))
  #theme(legend.position = "none",
  #       plot.title = element_text(face = "bold", hjust = .5))

discharge_locs

# Save Map
ggsave(discharge_locs, 
       filename = 'exports/discharge_stations.png',
       width = 5, height = 8)

```

## Plot locations of SSC sampling (in time period)

```{r ssc stations}
## Plot Station Data ##
wqp_plot<-wqp_stations%>%st_as_sf(coords=c('lon','lat')) %>% st_set_crs(4326)
ssc_locs <- ggplot() + 
  ## Basin and Channels ##
  geom_sf(data = riverdata$basin, show.legend = F) + 
  geom_sf(data = riverdata$UM_flowlines, col = "blue", show.legend = F) + 
  geom_sf(data = riverdata$UT_flowlines, col = "blue", alpha = .5, lwd=0.25, show.legend = F) + 
  theme_bw() +
  scale_size_continuous(range = c(1,7)) +
  
  ## Upper main channel#
  geom_sf(data = wqp_plot, aes(color=channel, shape=channel, size=channel),  fill = NA, stroke = 0.75) + 
  #scale_size_continuous(range = c(1,7)) +
  #scale_color_brewer(palette = "Set1") +
  scale_color_manual(values = c('green', 'red')) +
  scale_shape_manual(values = c(21, 1)) +
  scale_size_manual(values = c(3, 1)) +
  #theme_void() +
  coord_sf(label_graticule = 'NESW') +
  labs(title = "USGS Station Locations Measuring SSC",
       caption = paste0(startDate, ' to ', endDate))
  #theme(legend.position = "none",
  #       plot.title = element_text(face = "bold", hjust = .5))
ssc_locs

# Save Map
ggsave(ssc_locs, 
       filename = 'exports/ssc_sites.png',
       width = 5, height = 8)

```

## Plot dam locations and flowlines

```{r dam locations}
dam_flowline_map <- ggplot() + 
  ## Basin and Channels ##
  geom_sf(data = riverdata$basin) + 
  geom_sf(data = riverdata$UM_flowlines, col = "blue") + 
  geom_sf(data = riverdata$UT_flowlines, col = "blue", alpha = .5, lwd=0.25) + 
  theme_bw() +
  coord_sf(label_graticule = 'NESW') +
  geom_sf(data = basin_dams, 
          # Set size by storage capacity
          aes(size = Volume..Cubic.Yards.),
          color = 'red',
          shape = 2,
          fill = NA, stroke = 1) +# No fill, stroke (same as lwd for lines) is equal to 1 
  scale_size_continuous(range = c(0.5,3)) +
  labs(title = "NID Dam Locations")

dam_flowline_map

# Save Map
ggsave(dam_flowline_map, 
       filename = 'exports/dam_flowline_map.png',
       width = 5, height = 8)
```

## Import landsata data and harmonize with USGS data

```{r landsat import}
landsat_data <- data.table(read.csv(landsat_csv))[,':='(
  lat=Latitude,
  lon=Longitude
)][,.(SSC_mgL, month, year, distance_km, lat, lon)]

## Filter data to time of interest stamp ##
# Remember dates are in YYYY-MM-DD format
landsat_data_filter <- landsat_data %>% 
  # Filter by year
  filter(year<=as.numeric(substr(endDate, 1, 4))) %>%
  filter(year>=as.numeric(substr(startDate, 1, 4))) %>%
  # Filter by month for end years
  filter(!(year==as.numeric(substr(startDate, 1, 4)) & month<as.numeric(substr(startDate, 6, 7)))) %>%
  filter(!(year==as.numeric(substr(endDate, 1, 4)) & month>as.numeric(substr(endDate, 6, 7))))

### THEMES- From Evan Dethier ###
theme_facet <- theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_blank(),
    # panel.grid = element_blank(),
    # legend.position = 'none',
    panel.border = element_rect(size = 0.5),
    strip.background = element_rect(fill = 'white'),
    text = element_text(size=12),
    axis.text = element_text(size = 12), 
    plot.title = element_text(size = 13)
  )
season_facet <- theme_facet + theme(
  #legend.position = 'none', 
  strip.background = element_blank(),
  strip.text = element_text(hjust = 0, margin = margin(0,0,0,0, unit = 'pt'))
)

## Create Plots ##
ssc_landsat_plot <- ggplot(landsat_data_filter, aes(x = distance_km, y = SSC_mgL)) +
    stat_summary(geom = 'line', fun = 'mean') +
    season_facet +
    labs(title = 'SSC Concentration - Chattahoochee River',
         caption = paste0(startDate, ' to ', endDate),
         x = 'Distance Downstream (km)', 
         y = 'SSC (mg/L)')
ssc_landsat_plot

SSC_full$dist_downstream_km <- as.numeric(SSC_full$dist_downstream_km)
SSC_full$sscmgmL <- as.numeric(SSC_full$sscmgmL)

ssc_usgs_plot <- ggplot(data=drop_na(SSC_full), aes(x = dist_downstream_km, y = sscmgmL)) +
    geom_point() +
    stat_summary(
      geom = 'point',
      fun= 'mean',
      col = 'red',
      size = 3,
      shape = 24,
      fill = 'red') +
    season_facet +
    labs(title = 'SSC Concentration - Chattahoochee River',
         caption = paste0(startDate, ' to ', endDate),
         x = 'Distance Downstream (km)', 
         y = 'SSC (mg/L)')
ssc_usgs_plot

# Combine data into one dataframe for one plot
plot_data <- landsat_data_filter
usgs_dist <- drop_na(SSC_full)$dist_downstream_km
usgs_sscmgmL <- drop_na(SSC_full)$sscmgmL
plot_data <- qpcR:::cbind.na(plot_data, usgs_dist)
plot_data <- qpcR:::cbind.na(plot_data, usgs_sscmgmL)

ssc_combined <- 
    ggplot(plot_data, aes(x = distance_km, y = SSC_mgL)) +
      stat_summary(
        aes(x = distance_km, y = SSC_mgL),
        geom = 'line', 
        fun = 'mean',
        color = 'red') +
      #geom_point(data = drop_na(plot_data), aes(x = usgs_dist, y = usgs_sscmgmL)) +
        stat_summary(
                data = plot_data,
                aes(x = usgs_dist, y = usgs_sscmgmL),
                geom = 'errorbar',
                fun.data= mean_se,
                fun.args = list(mult = 1), # mult = # of standard errors
                size = 0.5,
                width =  30,
                color = 'green') +
        stat_summary(
          data = drop_na(plot_data),
          aes(x = usgs_dist, y = usgs_sscmgmL),
          geom = 'point',
          fun= 'mean',
          col = 'purple',
          size = 3,
          shape = 24,
          fill = 'purple') +
      season_facet +
      #scale_y_continuous(limits = c(0, 1000)) + # IGNORING SOME OUTLIERS
      labs(title = 'SSC Concentration - Chattahoochee River',
           caption = paste0(startDate, ' to ', endDate),
           x = 'Distance Downstream (km)', 
           y = 'SSC (mg/L)')

ssc_combined
```
