---
title: "SSC_Retrieval"
output: github_document
author: "Ilan Valencius"
date: "2022-06-16"
---

# Use: "For retrieving USGS suspended sediment concentration and discharge data along a river transect and integrating with landsat derived SSC measurements"

## Import Packages

```{r packages}
library(dataRetrieval)
library(sp)
library(sf)
library(maptools)
library(magrittr)
library(maps)
library(rgdal)
library(ggplot2)
library(usmap)
library(stringr)
library(dataRetrieval)
library(dplyr)
library(patchwork)
library(dams)
library(data.table)
library(nhdplusTools)
library(riverdist)
library(GISTools)
library(rgeos)
library(tidyr)
library(qpcR)
library(scales)
library(vioplot)
library(raster)
library(units)
```

## Set up imports

-   00060: discharge, cubic feet per second
-   80154: Suspended sediment concentration, milligrams per liter
-   Dates should be in in YYYY-MM-DD format

```{r imports}
wd_root <- 'D:/valencig/Thesis/USGS_dataquery'
centerline_kml <- "D:/valencig/Thesis/Data/chattahoochee_shape/chattahoochee_centerline.kml"

# Location of dams saved as kml files in dam_read_dir
# dam_names <- paste0(c("Buford Dam",
#                       "Morgan Falls",
#                       "Langdale Dam",
#                       "Eagle and Phoenix Dam",
#                       "West Point Dam",
#                       "Riverview Dam",
#                       "Bartletts Ferry Dam",
#                       "Goat Rock Dam",
#                       "Oliver Dam",
#                       "North Highlands Dam",
#                       "Walter F. George Dam",
#                       "George W Andrew Lock and Dam",
#                       "Jim Woodruff Dam"), ".kml")
# dam_read_dir <- "D:/valencig/Thesis/Data/chattahoochee_shape/dams/"

# When you want station info
startDate <- "1985-01-01"
endDate <- "2023-01-01"

## Query parameters for station data ##

# Daily value parameters
dv_parameters <- c("00060")
# Water quality parameters
wq_parameters <- c("80154") #(SSC, mgL)
# for WQP portal, characteristic name is hardcoded in
# Stat Codes
statCd <- c("00003") # stat code: mean

## If using station numbers from file ##

# 8 digit station numbers of interest, column name must be 'site_no'
station_file <- "D:/valencig/Thesis/USGS_dataquery/imports/station_numbers.csv"
usgs_prefix <- FALSE # do station numbers have 'USGS-' in title

## If getting station data from transect ##
upstream_distance_km <- 686

## Dam info ## 
use_dam_file <- TRUE # if set to false will autoquery data from NID website
dam_file <- 'D:/valencig/Thesis/USGS_dataquery/imports/nation.csv'

## Predicted SSC from landsat ##
landsat_csv <- 'D:/valencig/Thesis/chattahoochee-dams/chattahoochee-dams-exports/SSC_pred.csv'

## Don't touch this code ##

# helper function -> pads a character string with leading 0s (for USGS codes)
pad0 <- function(x) {
  while (nchar(x) < 8) {
    x <- paste0("0", x)
  }
  return(x)
}

centerline <- as.data.frame(maptools::getKMLcoordinates(centerline_kml, 
                                                        ignoreAltitude = TRUE))
names(centerline) <- c('lon','lat')
# Convert centerline to sf for plotting
centerline_sf <- st_as_sf(centerline, coords=c("lon","lat")) %>% st_set_crs(4326)

wd_root <- paste0(wd_root, '/', startDate, '_', endDate)
if(!dir.exists(wd_root)){
    dir.create(wd_root)
}
```

## Plot centerline transect

```{r transect}
# plot_dam <- function(dam_name){
#   dam <- as.data.frame(t(as.data.frame(maptools::getKMLcoordinates(paste0(dam_read_dir, dam_name),
#                                                         ignoreAltitude = TRUE))))
#   names(dam) <- c('lon','lat')
#   dam_transform <- usmap_transform(dam)
#   geom_point(data = dam_transform,
#              aes(x = x, y = y),
#              color = "green",
#              shape=2)
# }
# 
# centerline_transform <- usmap_transform(centerline)
# 
# # Create Dam Map
# dam_map = plot_usmap(fill = "black", alpha = 0.5, color = "white", size = 1,
#            include= c("GA","FL", "AL"), labels = TRUE) +
#   labs(title = "Chattahooche Centerline", subtitle = "Buford Dam to Brothers River") +
#   geom_path(data = centerline_transform,
#             aes(x = x, y = y),
#             color = "red",
#             size = 1) +
#   lapply(dam_names, plot_dam)
# 
# dam_map
# 
# # Save Map
# ggsave(dam_map,
#        filename = 'exports/rivertransect.png',
#        width = 5, height = 8)

```

## Get station info and plot station locations (from file)

```{r station plot}
# Function to remove empty columns of query
# rm_empty <- function(data){
#   empty_columns <- colSums(is.na(data) | data == "") == nrow(data)
#   return(data[, !empty_columns])
# }
# stations <- read.csv(station_file,colClasses=c("character")) # read as character to keep leading zeros
# if (usgs_prefix) {
#   # remove USGS-prefix
#   station_nums <- unlist(strsplit(stations$site_no, split='-'))[c(FALSE, TRUE)]
# } else {
#   station_nums <- stations$site_no
# }
# station_nums <- unlist(lapply(station_nums, pad0))
# station_data <- readNWISsite(station_nums)
# station_data <- rm_empty(station_data)

# To export information on stations to csv
# write.csv(station_data, "exports/valencius_chattahoochee_usgs_stations.csv", row.names=FALSE)
# 
# station_transform = usmap_transform(station_data, 
#                                       input_names = c("dec_long_va", "dec_lat_va"))
# 
# station_map <- plot_usmap(fill = "black", alpha = 0.5, color = "white", size = 1, 
#            include= c("GA","FL", "AL"), labels = TRUE) +
#   labs(title = "USGS Station Locations") +
#   geom_path(data = centerline_transform,
#             aes(x = x, y = y),
#             color = "red",
#             size = 1) +
#   geom_point(data = station_transform,
#               aes(x = x, y = y),
#               color = "yellow",
#              shape=4)
# 
# station_map

# Save Map
# ggsave(station_map,
#        filename = 'exports/valencius_stationlocs.png',
#        width = 5, height = 8)
```

## Query each station (from file)

```{r station info}
## Get daily discharge data ##
# dv <- readNWISdv(station_nums, dv_parameters, startDate, endDate, statCd = statCd)
# dv_filtered <- data.frame(dv["site_no"], 
#                           dv["Date"],
#                           dv["X_00060_00003"]) # X_00060_00003 will need to change depending on your stat codes
## Get water quality data ##
# wq <- readWQPqw(paste0("USGS-", station_nums), wq_parameters, startDate, endDate)

#stations <- read.table(station_file, header = TRUE, colClasses = "character")

## Get daily discharge data ##
# names(dv_filtered) <- c("site_no", "date", "discharge")

# Strip 'USGS-' identifier from station numbers
# wq["MonitoringLocationIdentifier"] <- lapply(list(wq[["MonitoringLocationIdentifier"]]), substring,
#                                                first = 6)
# wq_filtered <- data.frame(wq["MonitoringLocationIdentifier"],
#                             wq["ActivityStartDate"],
#                             wq["ResultMeasureValue"])
# names(wq_filtered) <- c("site_no","date", "sscmgL")
## To export station data to csv ##
# write.csv(dv_filtered, "exports/stations_from_file/valencius_discharge.csv", row.names=FALSE)
# write.csv(wq_filtered, "exports/stations_from_file/valencius_ssc.csv", row.names=FALSE)
```

## Automatically extract SSC and Q from stations

-   **Note:** this may take a while

```{r load data}
## Run if you have previously saved data from {r get basin} ##
save_dir <- paste0(wd_root, '/variables/')
load(file=paste0(save_dir, 'riverdata.Rdata'))
load(file=paste0(save_dir, 'nwis_stations.Rdata'))
load(file=paste0(save_dir, 'wqp_stations.Rdata'))
load(file=paste0(save_dir, 'SSC_full.Rdata'))
load(file=paste0(save_dir, 'Q_full.Rdata'))
```

```{r fix line2network fxn}
line2network <- function (sp = NA, path = ".", layer = NA, tolerance = 100, 
  reproject = NULL, supplyprojection = NULL) 
{
  if (suppressWarnings(is.na(sp))) {
    sp <- suppressWarnings(rgdal::readOGR(dsn = path, layer = layer, 
      verbose = F))
  }
  if (class(sp) != "SpatialLinesDataFrame") {
    stop("Specified shapefile is not a linear feature.")
  }
  if (is.na(sp@proj4string@projargs) & !is.null(supplyprojection)) {
    sp@proj4string@projargs <- supplyprojection
  }
  if (is.na(sp@proj4string@projargs)) {
    stop("Shapefile projection information is missing.  Use supplyprojection= to specify a Proj.4 projection to use.  If the input shapefile is in WGS84 geographic (long-lat) coordinates, this will be +proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 (in double-quotes).  If so, it must also be reprojected using reproject=.")
  }
  proj4 <- strsplit(sp@proj4string@projargs, split = " ")
  projected <- sp::is.projected(sp)
  if (is.null(reproject) & !projected) 
    stop("Distances can only be computed from a projected coordinate system.  Use reproject= to specify a Proj.4 projection to use.")
  if (!is.null(reproject)) {
    sp <- sp::spTransform(sp, sp::CRS(reproject))
    proj4 <- strsplit(sp@proj4string@projargs, split = " ")
  }
  units <- "unknown"
  for (i in 1:length(proj4[[1]])) {
    if (proj4[[1]][i] != "") {
      proj4arg <- strsplit(proj4[[1]][i], split = "=")
      if (proj4arg[[1]][1] == "+units") {
        units <- proj4arg[[1]][2]
        cat("\n", "Units:", proj4arg[[1]][2], "\n")
      }
    }
  }
  if (length(sp@lines) > 1) {
    sp_line <- NA
    sp_seg <- NA
    lines <- list()
    j <- 1
    for (i in 1:length(sp@lines)) {
      for (k in 1:length(sp@lines[i][[1]]@Lines)) {
        lines[[j]] <- sp@lines[i][[1]]@Lines[[k]]@coords
        sp_line[j] <- i
        sp_seg[j] <- k
        j <- j + 1
      }
    }
  }
  if (length(sp@lines) == 1) {
    lines <- sp@lines[1][[1]]@Lines
    length <- length(lines)
    lines.new <- list()
    for (i in 1:length) {
      lines.new[[i]] <- lines[[i]]@coords
    }
    lines <- lines.new
    sp_line <- rep(1, length)
    sp_seg <- 1:length
  }
  length <- length(lines)
  rivID <- 1:length
  lineID <- data.frame(rivID, sp_line, sp_seg)
  connections <- calculateconnections(lines = lines, tolerance = tolerance)
  if (any(connections %in% 5:6)) 
    braided <- TRUE
  lengths <- rep(NA, length)
  for (i in 1:length) {
    lengths[i] <- pdisttot(lines[[i]])
  }
  names <- rep(NA, length)
  mouth.seg <- NA
  mouth.vert <- NA
  mouth <- list(mouth.seg, mouth.vert)
  names(mouth) <- c("mouth.seg", "mouth.vert")
  sequenced <- FALSE
  braided <- NA
  cumuldist <- list()
  for (i in 1:length) {
    xy <- lines[[i]]
    n <- dim(xy)[1]
    cumuldist[[i]] <- c(0, cumsum(sqrt(((xy[1:(n - 1), 1] - 
      xy[2:n, 1])^2) + ((xy[1:(n - 1), 2] - xy[2:n, 2])^2))))
  }
  out.names <- c("sp", "lineID", "lines", "connections", "lengths", 
    "names", "mouth", "sequenced", "tolerance", "units", 
    "braided", "cumuldist")
  out <- list(sp, lineID, lines, connections, lengths, names, 
    mouth, sequenced, tolerance, units, braided, cumuldist)
  names(out) <- out.names
  class(out) <- "rivernetwork"
  length1 <- length(out$lengths)
  length2 <- length(out$lengths)
  if (length2 < length1) 
    cat("\n", "Removed", length1 - length2, "duplicate segments.", 
      "\n")
  length3 <- length(out$lengths)
  if (length3 < length2) 
    cat("\n", "Removed", length2 - length3, "segments with lengths shorter than the connectivity tolerance.", 
      "\n")
  return(out)
}
```

```{r station extract}
save_dir <- paste0(wd_root,'/variables/')
if(!dir.exists(save_dir)){
    dir.create(save_dir)
}
if(!dir.exists(paste0(wd_root,'/exports/'))){
    dir.create(paste0(wd_root,'/exports/'))
}
## Determine Watershed Geometries ##
summarize.nldi = function(input){
  data.frame(name = names(input), 
             class = sapply(input, class)[1], 
             row.names = NULL) %>% 
    mutate(feature_count = ifelse(class == "sf", sapply(input, nrow), 
                                  sapply(input, length)))
}
# Get last lat, long pair from centerline
start_loc <- tail(centerline, 1)
start_loc <- c(start_loc[[1]], start_loc[[2]]) 
riverdata <- findNLDI(location = start_loc,
              nav = c("UT", "UM"),
              find = c("nwis", "WQP","basin", "flowlines"),
              distance_km = upstream_distance_km)

summarize.nldi(riverdata)

## Merge Site Names ##
# get all WQP sites
mc_names <- paste0("USGS-",lapply(riverdata$UM_WQP$comid, pad0))
ut_names <- paste0("USGS-",lapply(riverdata$UT_WQP$comid, pad0))
# merge with nwis sites
mc_names <- unique(append(mc_names, riverdata$UM_nwissite$identifier))
ut_names <- unique(append(ut_names, riverdata$UT_nwissite$identifier))

# Remove mislabelled sites outside of the watershed (remove from ut and mc) 
mc_names <- mc_names[- match("USGS-02297310",mc_names)]
mc_names <- mc_names[- match("USGS-02297272",mc_names)]
mc_names <- mc_names[- match("USGS-03298550",mc_names)]
ut_names <- ut_names[- match("USGS-02297310",ut_names)]
ut_names <- ut_names[- match("USGS-02297272",ut_names)]
ut_names <- ut_names[- match("USGS-03298550",ut_names)]
ut_names <- ut_names[- match("USGS-02296750",ut_names)]
ut_names <- ut_names[- match("USGS-02047783",ut_names)]
ut_names <- ut_names[- match("USGS-03435970",ut_names)]
ut_names <- ut_names[- match("USGS-03291310",ut_names)]
ut_names <- ut_names[- match("USGS-03437900",ut_names)]
ut_names <- ut_names[- match("USGS-02130840",ut_names)]
ut_names <- ut_names[- match("USGS-02308865",ut_names)]
ut_names <- ut_names[- match("USGS-02349900",ut_names)]
ut_names <- ut_names[- match("USGS-02350080",ut_names)]

## Get Dicharge Data ##riverdata$UM_nwissite$identifier
Q_mc <- data.table(readNWISdv(gsub("USGS-", "", mc_names), 
                parameterCd = dv_parameters, 
                startDate = startDate,
                endDate = endDate) %>% renameNWISColumns())[,":=" (
                  site_no = paste0("USGS-", site_no),
                  date = Date,
                  flow = Flow,
                  portal = 'NWIS',
                  channel = 'MAIN STEM'
                )][,.(site_no, date, flow, portal, channel)]
Q_ut <- data.table(readNWISdv(gsub("USGS-", "", ut_names), 
                parameterCd = dv_parameters, 
                startDate = startDate,
                endDate = endDate) %>% renameNWISColumns())[,":=" (
                  site_no = paste0("USGS-", site_no),
                  date = Date,
                  flow = Flow,
                  portal = 'NWIS',
                  channel = 'TRIBUTARY'
                )][,.(site_no, date, flow, portal, channel)]

# Remove main channel sites from ut sites
Q_ut <- anti_join(Q_ut, Q_mc, by="site_no")

## Get SSC data ##
SSC_wqp_mc <- data.table(readWQPdata(siteNumbers=mc_names, 
                parameterCd = wq_parameters,
                startDate=startDate,
                endDate=endDate
                ))[,":=" (
                  site_no = MonitoringLocationIdentifier,
                  date = ActivityStartDate,
                  sscmg_L = ResultMeasureValue,
                  portal = 'WQP',
                  channel = 'MAIN STEM'
                )][,.(site_no, date, sscmg_L, portal, channel)]

# May need to save as a few different variables (ex foo1, foo2, foo3) and rbind() 
# because WQP can't handle large requests (limit to 1000 site numbers at a time)
SSC_wqp_ut <- data.table(readWQPdata(siteNumbers=ut_names, 
                parameterCd = wq_parameters,
                startDate = startDate,
                endDate = endDate
                ))[,":=" (
                  site_no = MonitoringLocationIdentifier,
                  date = ActivityStartDate,
                  sscmg_L = ResultMeasureValue,
                  portal = 'WQP',
                  channel = 'TRIBUTARY'
                )][,.(site_no, date, sscmg_L, portal, channel)]

# Remove main channel sites from ut sites
SSC_wqp_ut <- anti_join(SSC_wqp_ut, SSC_wqp_mc, by="site_no")

## Combine upper tributaries and main channel ##
Q_full <- rbind(Q_mc, Q_ut)
SSC_full <- rbind(SSC_wqp_mc, SSC_wqp_ut)

## Identify Stations of Interest ##
# NWIS sites
mc_nwis_names <- unique(Q_mc$site_no)
ut_nwis_names <- unique(Q_ut$site_no)

mc_nwis <- data.table(whatNWISsites(site=gsub("USGS-", "",mc_nwis_names)))[,":="(
    portal = "NWIS",
    site_no = paste0("USGS-", site_no),
    lat = dec_lat_va,
    lon = dec_long_va,
    channel="MAIN STEM"
  )][,.(portal, site_no, station_nm,site_tp_cd, lat, lon, channel)]
ut_nwis <- data.table(whatNWISsites(site=gsub("USGS-", "",ut_nwis_names)))[,":="(
    portal = "NWIS",
    site_no = paste0("USGS-", site_no),
    lat = dec_lat_va,
    lon = dec_long_va,
    channel="TRIBUTARY"
  )][,.(portal, site_no, station_nm,site_tp_cd, lat, lon, channel)]

# WQP sites
mc_wqp_names <- unique(SSC_wqp_mc$site_no)
ut_wqp_names <- unique(SSC_wqp_ut$site_no)

mc_wqp <- data.table(whatWQPsites(siteid=mc_wqp_names))[,":="(
    portal = "WQP",
    site_no = MonitoringLocationIdentifier,
    station_nm = MonitoringLocationName,
    site_code = MonitoringLocationTypeName,
    drainage_area_km2 = DrainageAreaMeasure.MeasureValue*(2.58999/1.00000073), # sq mi -> sq km
    lat = LatitudeMeasure,
    lon = LongitudeMeasure,
    elevation_m = VerticalMeasure.MeasureValue *0.3048, # ft -> m
    channel="MAIN STEM"
  )][,.(portal, site_no, station_nm, site_code, lat, lon, drainage_area_km2, elevation_m, channel)]

ut_wqp <- data.table(whatWQPsites(siteid=ut_wqp_names))[,":="(
    portal = "WQP",
    site_no = MonitoringLocationIdentifier,
    station_nm = MonitoringLocationName,
    site_code = MonitoringLocationTypeName,
    drainage_area_km2 = DrainageAreaMeasure.MeasureValue*(2.58999/1.00000073), # sq mi -> sq km
    lat = LatitudeMeasure,
    lon = LongitudeMeasure,
    elevation_m = VerticalMeasure.MeasureValue *0.3048, # ft -> m
    channel="TRIBUTARY"
  )][,.(portal, site_no, station_nm, site_code, lat, lon, drainage_area_km2, elevation_m, channel)]  

## Map gauge location to river distance ##
# trace(line2network, edit=T) --> comment out following two lines
# suppressMessages(out <- removemicrosegs(out))
# suppressMessages(out <- removeduplicates(out))
S1 <- as(riverdata$UM_flowlines, 'Spatial')
nldi_proj4 <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84"
AKalbers <- "+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154
    +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +ellps=GRS80 +towgs84=0,0,0"
river_center <- line2network(S1, reproject=AKalbers)

# Apply projection to mc nwis sites then convert into meter projection
mc_nwis_spatial <- mc_nwis
mc_nwis_spatial$lat <- as.numeric(mc_nwis_spatial$lat)
mc_nwis_spatial$lon <- as.numeric(mc_nwis_spatial$lon)
coordinates(mc_nwis_spatial) <- ~lon + lat
proj4string(mc_nwis_spatial) <- '+init=epsg:4326'
mc_nwis_spatial <- spTransform(mc_nwis_spatial, CRS(AKalbers))
mc_nwis_spatial <- as.data.frame(mc_nwis_spatial)
nwis_riv <- xy2segvert(x=mc_nwis_spatial$lon, y=mc_nwis_spatial$lat, rivers=river_center)

# Do the same for mc wqp sites
mc_wqp_spatial <- mc_wqp
mc_wqp_spatial$lat <- as.numeric(mc_wqp_spatial$lat)
mc_wqp_spatial$lon <- as.numeric(mc_wqp_spatial$lon)
coordinates(mc_wqp_spatial) <- ~lon + lat
proj4string(mc_wqp_spatial) <- '+init=epsg:4326'
mc_wqp_spatial <- spTransform(mc_wqp_spatial, CRS(AKalbers))
mc_wqp_spatial <- as.data.frame(mc_wqp_spatial)
wqp_riv <- xy2segvert(x=mc_wqp_spatial$lon, y=mc_wqp_spatial$lat, rivers=river_center)

# Determine distance from start of channel for nwis sites
distances_nwis <- list()
for (i in 1:length(nwis_riv$vert)){
  # Distance to mouth of river
  dist_m <- riverdistance(startseg = nwis_riv$seg[i], startvert = nwis_riv$vert[i],
                            endvert = 1, endseg = 1, rivers=river_center)
  # Convert from degrees to km
  distances_nwis <- append(distances_nwis, upstream_distance_km-dist_m/1000)
}
nwis_riv$dist_downstream_km <- distances_nwis

# Determine distance from start of channel for wqp sites
distances_wqp <- list()
for (i in 1:length(wqp_riv$vert)){
  # Distance to mouth of river
  dist_m <- riverdistance(startseg = wqp_riv$seg[i], startvert = wqp_riv$vert[i],
                            endvert = 1, endseg = 1, rivers=river_center)
  # Convert from degrees to km
  distances_wqp <- append(distances_wqp, upstream_distance_km-dist_m/1000)
}
wqp_riv$dist_downstream_km <- distances_wqp

## Merge station info ##
mc_nwis$dist2river_m <- nwis_riv$snapdist
mc_nwis$dist_downstream_km <- nwis_riv$dist_downstream_km
mc_wqp$dist2river_m <- wqp_riv$snapdist
mc_wqp$dist_downstream_km <- wqp_riv$dist_downstream_km

nwis_stations <- rbind(mc_nwis, ut_nwis, fill=TRUE)
wqp_stations <- rbind(mc_wqp, ut_wqp, fill=TRUE)

## Map station distances to Q and SSC measurements ##
Q_full <- left_join(Q_full, nwis_stations)
SSC_full <- left_join(SSC_full, wqp_stations)

## Convert variable data tables to upper case ##
nwis_stations <- mutate_all(nwis_stations, toupper)
wqp_stations <- mutate_all(wqp_stations, toupper)
Q_full <- mutate_all(Q_full, toupper)
SSC_full <- mutate_all(SSC_full, toupper)

## Save variables to save time ##
save(riverdata, file=paste0(save_dir, 'riverdata.Rdata'))
save(nwis_stations, file=paste0(save_dir, 'nwis_stations.Rdata'))
save(wqp_stations, file=paste0(save_dir, 'wqp_stations.Rdata'))
save(SSC_full, file=paste0(save_dir, 'SSC_full.Rdata'))
save(Q_full, file=paste0(save_dir, 'Q_full.Rdata'))

## Export data to csv ##
write.csv(Q_full, paste0(wd_root,"/exports/Q_full.csv"), row.names=FALSE)
write.csv(SSC_full, paste0(wd_root,"/exports/SSC_full.csv"), row.names=FALSE)
write.csv(nwis_stations, paste0(wd_root, '/exports/Q_stations.csv'), row.names=FALSE)
write.csv(wqp_stations, paste0(wd_root, '/exports/SSC_stations.csv'), row.names=FALSE)
```

## Determine locations of all dams in the watershed

-   Dam data cane be queried automatically or downloaded in csv form from the NID Website [<https://nid.usace.army.mil/#/downloads>]
-   **Note:** If you download the nation.csv which contains all NID data, you must remove the first row which contains the last date the file was modified (R uses the first row as column names)

```{r dam query}
## Issue --> not all dams stored in NID database
## If importing from file ##
if (use_dam_file) {
  nid_dams <- read.csv(dam_file)
} else {
  ## CURRENTLY NOT WORKING
  nid_dams <- get_nid()
}

# Remove entries which are missing lat, lon
nid_dams <- na.omit(nid_dams, cols=c('Longitude','Latitude'))
# Convert to sf object
nid_dams_sf <- st_as_sf(nid_dams, coords = c("Longitude", "Latitude")) %>% st_set_crs(4326)

# Get dams in the basin
basin_dams <- st_intersection(nid_dams_sf,riverdata$basin$geometry)
```

# Start Making Plots

## Compare Centerline KML and NLDI

```{r NLDI sanity check}
centerline_compare <-
  ggplot() + 
    geom_sf(data = riverdata$basin) + 
    geom_sf(data = centerline_sf, col = "red", alpha = .5, size = 1)+
    theme_void() +
    labs(caption = "Input extent") +
  ggplot() +
    geom_sf(data = riverdata$basin, col = NA) + 
    geom_sf(data = riverdata$UM_flowlines, col = "blue",size = 1) +
    theme_void() +
    labs(title = "Centerlines",
         caption = "NLDI extent") + 
    theme(legend.position = "none",
           plot.title = element_text(face = "bold", hjust = .5))

centerline_compare

# Save Map
ggsave(centerline_compare, 
       filename = paste0(wd_root, '/exports/centerline_compare.png'),
       width = 5, height = 8)
```

## Plot all NWIS stations (time independent)

```{r NWIS stations}
## Plot Station Data ##
nwis_station_plot <- ggplot() + 
  ## Basin and Channels ##
  geom_sf(data = riverdata$basin) + 
  geom_sf(data = riverdata$UM_flowlines, col = "blue") + 
  geom_sf(data = riverdata$UT_flowlines, col = "blue", alpha = .5, lwd=0.25) + 
  theme_bw() +
  coord_sf(label_graticule = 'NESW') +
  
  geom_sf(data = riverdata$UM_nwissite, shape = 21, 
          fill = NA, stroke = 0.75, size = 1.5, color="red") + # Shape aes: USGS gage, set with scale_shape_manual
  geom_sf(data = riverdata$UT_nwissite, shape = 21, 
          fill = NA, stroke = 0.25, size = 0.5, color="red") + # Shape aes: USGS gage, set with scale_shape_manual 
  scale_size_continuous(range = c(1,7)) +
  scale_color_brewer(palette = "Set1") +
  #theme_void() +
  labs(title = "USGS Station Locations") + 
  theme(legend.position = "none",
         plot.title = element_text(face = "bold", hjust = .5))

nwis_station_plot

# Save Map
ggsave(nwis_station_plot,
       filename = paste0(wd_root, '/exports/usgs_stations.png'),
       width = 5, height = 8)
```

## Plot locations of USGS stations which measure discharge (in time period)

```{r discharge stations}
## Plot Station Data ##
nwis_plot <- nwis_stations%>%st_as_sf(coords=c('lon','lat')) %>% st_set_crs(4326)

discharge_locs <- ggplot() + 
  ## Basin and Channels ##
  geom_sf(data = riverdata$basin, show.legend = F) + 
  geom_sf(data = riverdata$UM_flowlines, col = "blue", show.legend = F) + 
  geom_sf(data = riverdata$UT_flowlines, col = "blue", alpha = .5, lwd=0.25, show.legend = F) + 
  theme_bw() +
  scale_size_continuous(range = c(1,7)) +
  
  ## Upper main channel#
  geom_sf(data = nwis_plot, aes(color=channel, shape=channel, size=channel),  fill = NA, stroke = 0.75) + 
  #scale_size_continuous(range = c(1,7)) +
  #scale_color_brewer(palette = "Set1") +
  scale_color_manual(values = c('green', 'red')) +
  scale_shape_manual(values = c(21, 1)) +
  scale_size_manual(values = c(3, 1)) +
  #theme_void() +
  coord_sf(label_graticule = 'NESW') +
  labs(title = "USGS Station Locations Measuring Discharge",
       caption = paste0(startDate, ' to ', endDate))
  #theme(legend.position = "none",
  #       plot.title = element_text(face = "bold", hjust = .5))

discharge_locs

# Save Map
ggsave(discharge_locs, 
       filename = paste0(wd_root, '/exports/discharge_stations.png'),
       width = 5, height = 8)

```

## Plot locations of SSC sampling (in time period)

```{r ssc stations}
## Plot Station Data ##
wqp_plot<-wqp_stations%>%st_as_sf(coords=c('lon','lat')) %>% st_set_crs(4326)

ssc_locs <- ggplot() + 
  ## Basin and Channels ##
  geom_sf(data = riverdata$basin, show.legend = F) + 
  geom_sf(data = riverdata$UM_flowlines, col = "blue", show.legend = F) + 
  geom_sf(data = riverdata$UT_flowlines, col = "blue", alpha = .5, lwd=0.25, show.legend = F) + 
  theme_bw() +
  scale_size_continuous(range = c(1,7)) +
  
  ## Upper main channel#
  geom_sf(data = wqp_plot, aes(color=channel, shape=channel, size=channel),  fill = NA, stroke = 0.75) + 
  #scale_size_continuous(range = c(1,7)) +
  #scale_color_brewer(palette = "Set1") +
  scale_color_manual(values = c('green', 'red')) +
  scale_shape_manual(values = c(21, 1)) +
  scale_size_manual(values = c(3, 1)) +
  #theme_void() +
  coord_sf(label_graticule = 'NESW') +
  labs(title = "USGS Station Locations Measuring SSC",
       caption = paste0(startDate, ' to ', endDate))
  #theme(legend.position = "none",
  #       plot.title = element_text(face = "bold", hjust = .5))
ssc_locs

# Save Map
ggsave(ssc_locs, 
       filename = paste0(wd_root, '/exports/ssc_sites.png'),
       width = 5, height = 8)

```

## Plot dam locations and flowlines

```{r dam locations}
dam_flowline_map <- ggplot() + 
  ## Basin and Channels ##
  geom_sf(data = riverdata$basin) + 
  geom_sf(data = riverdata$UM_flowlines, col = "blue") + 
  geom_sf(data = riverdata$UT_flowlines, col = "blue", alpha = .5, lwd=0.25) + 
  theme_bw() +
  coord_sf(label_graticule = 'NESW') +
  geom_sf(data = basin_dams, 
          # Set size by storage capacity
          aes(size = Volume..Cubic.Yards.),
          color = 'red',
          shape = 2,
          fill = NA, stroke = 1) +# No fill, stroke (same as lwd for lines) is equal to 1 
  scale_size_continuous(range = c(0.5,3)) +
  labs(title = "NID Dam Locations")

dam_flowline_map

# Save Map
ggsave(dam_flowline_map, 
       filename = paste0(wd_root, '/exports/dam_flowline_map.png'),
       width = 5, height = 8)
```

## Import landsata data and harmonize with USGS data

# ISSUE: NEED TO REDUCE BY DAY HERE --> actually I dont

```{r landsat import}
landsat_data <- data.table(read.csv(landsat_csv))[,':='(
  lat=Latitude,
  lon=Longitude,
  date=sample_dt
)][,.(SSC_mgL, date, year, distance_km, lat, lon)]

landsat_data$year_chunk <- cut(as.numeric(landsat_data$year), seq(from = 1985, to = 2026, by = 5), right=FALSE)
landsat_data <- landsat_data %>% mutate(SSC_mgL=replace(SSC_mgL, SSC_mgL>=10000, NA))

## Filter data to time of interest stamp ##
# Remember dates are in YYYY-MM-DD format
landsat_data_filter <- landsat_data %>% 
  filter(as.Date(date)>=as.Date(startDate)) %>%
  filter(as.Date(date)<=as.Date(endDate))
  # # Filter by year
  # filter(year<=as.numeric(substr(endDate, 1, 4))) %>%
  # filter(year>=as.numeric(substr(startDate, 1, 4))) %>%
  # # Filter by month for end years
  # filter(!(year==as.numeric(substr(startDate, 1, 4)) & month<as.numeric(substr(startDate, 6, 7)))) %>%
  # filter(!(year==as.numeric(substr(endDate, 1, 4)) & month>as.numeric(substr(endDate, 6, 7))))

### THEMES- From Evan Dethier ###
theme_facet <- theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_blank(),
    # panel.grid = element_blank(),
    # legend.position = 'none',
    panel.border = element_rect(size = 0.5),
    strip.background = element_rect(fill = 'white'),
    text = element_text(size=12),
    axis.text = element_text(size = 12), 
    plot.title = element_text(size = 13)
  )

season_facet <- theme_facet + theme(
  #legend.position = 'none', 
  strip.background = element_blank(),
  strip.text = element_text(hjust = 0, margin = margin(0,0,0,0, unit = 'pt'))
)

lm_eqn <- function(m){
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(unname(coef(m)[1]), digits = 4),
                        b = format(unname(coef(m)[2]), digits = 4),
                        r2 = format(summary(m)$r.squared, digits = 4)))
  as.character(as.expression(eq));
}
```

# Start making plots

```{r}
SSC_full$dist_downstream_km <- as.numeric(SSC_full$dist_downstream_km)
SSC_full$sscmg_L <- as.numeric(SSC_full$sscmg_L)

## Create Plots ##
ssc_landsat_plot <- ggplot(landsat_data_filter, aes(x = distance_km, y = SSC_mgL)) +
    stat_summary(geom = 'line', fun = 'mean') +
    season_facet +
    labs(title = 'SSC Concentration - Chattahoochee River',
         caption = paste0(startDate, ' to ', endDate),
         x = 'Distance Downstream (km)', 
         y = 'SSC (mg/L)')
ssc_landsat_plot

ssc_usgs_plot <- ggplot(data=drop_na(SSC_full), aes(x = dist_downstream_km, y = sscmg_L)) +
    geom_point() +
    stat_summary(
      geom = 'point',
      fun= 'mean',
      col = 'red',
      size = 3,
      shape = 24,
      fill = 'red',
      na.rm=T) +
    season_facet +
    labs(title = 'SSC Concentration - Chattahoochee River',
         caption = paste0(startDate, ' to ', endDate),
         x = 'Distance Downstream (km)', 
         y = 'SSC (mg/L)')
ssc_usgs_plot

# Combine data into one dataframe for one plot
# plot_data <- landsat_data_filter
# usgs_dist <- drop_na(SSC_full)$dist_downstream_km
# usgs_sscmg_L <- drop_na(SSC_full)$sscmg_L
# plot_data <- qpcR:::cbind.na(plot_data, usgs_dist)
# plot_data <- qpcR:::cbind.na(plot_data, usgs_sscmg_L)
# plot_data$year_chunk <- cut(as.numeric(plot_data$year), seq(from = 1985, to = 2026, by = 5), right=FALSE)

SSC_main <- SSC_full %>% filter(channel == 'MAIN STEM')
SSC_main$year_chunk <- cut(as.numeric(format(as.Date(SSC_main$date), "%Y")), seq(from = 1985, to = 2026, by = 5), right=FALSE)
# Get mean usgs ssc for each year
# Need to get mean for each distance then across the whole transect
ssc_mean <- data.table(year_chunk = unique(SSC_main$year_chunk), MN = as.numeric()) %>% arrange(year_chunk)
ssc_mean$false_int <- c(1,2,3,4,5,6,7,8)

for (year_subset in unique(landsat_data_filter$year_chunk)){
  year_data <- landsat_data_filter %>% filter(year_chunk == year_subset)
  x_means <-  year_data %>% group_by(distance_km) %>% summarize(x_ssc = mean(SSC_mgL, na.rm=T))
  ssc_mean[ssc_mean$year_chunk==year_subset,]$MN <- mean(x_means$x_ssc)
}

# plot_data
ssc_combined <- 
    ggplot(landsat_data_filter, aes(x = distance_km, y = SSC_mgL)) +
      stat_summary(
        aes(x = distance_km, y = SSC_mgL, color='Landsat Derived Mean SSC'),
        geom = 'line', 
        fun = 'mean',
        inherit.aes = FALSE,
        show.legend=TRUE,
        na.rm=T) +
      #geom_point(data = drop_na(plot_data), aes(x = usgs_dist, y = usgs_sscmg_L)) +
        stat_summary(
          data = SSC_main,
          aes(x = dist_downstream_km, y = sscmg_L, color='1 standard Error'),
          geom = 'errorbar',
          fun.data= mean_se,
          fun.args = list(mult = 1), # mult = # of standard errors
          size = 0.5,
          width =  30,
          #color = 'green',
          inherit.aes = FALSE,
          show.legend=TRUE,
          na.rm=T) +
        stat_summary(
          data = SSC_main,
          aes(x = dist_downstream_km, y = sscmg_L, color='USGS Derived Mean SSC'),
          geom = 'point',
          fun= 'mean',
          #size = 3,
          #shape=24,
          inherit.aes = FALSE,
          show.legend=TRUE,
          fill = 'purple',
          na.rm=T) +
        stat_summary(
          data = SSC_main,
          aes(x = dist_downstream_km, y = sscmg_L, color='USGS Derived Mean SSC'),
          geom = 'line',
          fun= 'mean',
          #size = 3,
          #shape=24,
          inherit.aes = FALSE,
          show.legend=TRUE,
          na.rm=T) +
      # Mean value of USGS ssc
      geom_hline(data=ssc_mean, aes(yintercept = MN, color='Mean Landsat SSC for whole transect'), linetype="dotted") +
      season_facet +
      facet_wrap(~year_chunk, scales = "free_y") +
      theme(
        legend.position = "bottom"
      ) +
      guides(color=guide_legend("Key")) +
      scale_color_manual(values = c("green", "red", "black","#5ab4ac")) +
      labs(title = 'SSC Concentration - Chattahoochee River',
           caption = paste0(startDate, ' to ', endDate),
           x = 'Distance Downstream (km)', 
           y = 'SSC (mg/L)')

ssc_combined

# Plot mean SSC over time
lm_ssc <- function(df){
    m <- lm(MN ~ false_int, df);
    eq <- substitute(italic('Mean SSC') == b %.% italic('(Years since 1985)/5')+a*","~~italic(r)^2~"="~r2, 
         list(a = format(unname(coef(m)[1]), digits = 2),
              b = format(unname(coef(m)[2]), digits = 2),
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));
}

mean_ssc_plot <- ggplot(data = ssc_mean, aes(x=year_chunk, y=MN)) +
  geom_line(group=1) +
  geom_smooth(mapping=aes(x=false_int, y=MN), method = "lm", se=FALSE, color="red", formula = y ~ x) +
  geom_label(x = 6, y = 55, label = lm_ssc(ssc_mean), parse = T) +
  season_facet +
  labs(title='Landsat Derived Mean SSC Along Chattahoochee Transect',
       x='Year Grouping',
       y='Average SSC (mg/L)')

mean_ssc_plot

## Save combined plot ##
ggsave(ssc_combined, 
       filename = paste0(wd_root, '/exports/ssc_USGSxLandsat.png'),
       width = 12, height = 6)

## Save mean_ssc plot ##
ggsave(mean_ssc_plot, 
       filename = paste0(wd_root, '/exports/landsat_mean_ssc.png'),
       width = 12, height = 6)

```

## Investigate SSC flux at the mouth of the river

```{r SSC flux (mouth)}
# Prepare Q data
Q_full_mc <- Q_full %>% filter(channel=='MAIN STEM')
Q_full_mc$year_chunk <- cut(as.numeric(format(as.Date(Q_full_mc$date), "%Y")), seq(from = 1985, to = 2026, by = 5), right=FALSE)
Q_full_mc$flow <- as.numeric(Q_full_mc$flow)
Q_full_mc$dist_downstream_km <- as.integer(as.numeric(Q_full_mc$dist_downstream_km))

# Prepare SSC data
SSC_full_mc <- SSC_full %>% filter(channel=='MAIN STEM')
SSC_full_mc$year_chunk <- cut(as.numeric(format(as.Date(SSC_full_mc$date), "%Y")), seq(from = 1985, to = 2026, by = 5), right=FALSE)
SSC_full_mc$sscmg_L <- as.numeric(SSC_full_mc$sscmg_L)
SSC_full_mc$dist_downstream_km <- as.integer(as.numeric(SSC_full_mc$dist_downstream_km))

# List unique ssc distances/q distances to create a rating curve
q_dists <- unique(Q_full_mc$dist_downstream_km)
ssc_dists <- unique(SSC_full_mc$dist_downstream_km)
similar_dists <- sort(intersect(q_dists, ssc_dists))
last_dist <- similar_dists[length(similar_dists)]

# Get station number at that distance
mouth_site <- SSC_full_mc[dist_downstream_km==last_dist,][1]$site_no
mouth_ssc <- SSC_full_mc %>% filter(site_no==mouth_site)
mouth_q <- Q_full_mc %>% filter(site_no==mouth_site)

# Need to convert  flow ft^3/2 to m^3/2
mouth_q$flow_m3s <- mouth_q$flow * 0.02832

# Create training data
ssc_q <- left_join(mouth_ssc, dplyr::select(mouth_q, c(date, flow_m3s)), by= "date")
ssc_q$SSC_flux_MTyr <- ssc_q$flow_m3s * ssc_q$sscmg_L * 3.10585 * 10**-5
ssc_q$log10_SSC_flux_MTyr <- log10(ssc_q$SSC_flux_MTyr)
ssc_q$log10_discharge_m3s  <- log10(ssc_q$flow_m3s)

# To get accurate means reduce to get average per day then average over the whole year
ssc_day_avg <- ssc_q %>% group_by(date) %>% 
  summarise_at(c("SSC_flux_MTyr","log10_SSC_flux_MTyr","log10_discharge_m3s","flow_m3s","sscmg_L"), mean) %>%
  left_join(subset(ssc_q, 
                   select=-c(SSC_flux_MTyr, log10_SSC_flux_MTyr, log10_discharge_m3s, flow_m3s, sscmg_L)), by="date") %>%
  distinct()

# Save training data
write.csv(ssc_q, paste0(wd_root,"/exports/", mouth_site,".csv"), row.names=FALSE)
write.csv(ssc_day_avg, paste0(wd_root,"/exports/", mouth_site,"_reduced_by_day.csv"), row.names=FALSE)

# Create flux plot not on rating curve
ssc_flux <- ggplot(ssc_day_avg, aes(x=format(as.Date(ssc_day_avg$date), "%Y"), y=SSC_flux_MTyr)) +
  # geom_point() +
  stat_summary(geom = 'line', fun = 'mean', group=1, aes(color="Average SSC Flux (MT/yr)")) +
  stat_summary(geom = 'errorbar', aes(color='1 standard Error'), fun.data= mean_se,
               fun.args = list(mult = 1), # mult = # of standard errors
               size = 0.5,
               width =  0.2,
               show.legend=TRUE) +
  # coord_cartesian(ylim=c(0,3)) +
  scale_color_manual(values = c("green", "red")) +
  season_facet +
  labs(title="SSC Flux at the Mouth of \nthe Chattahoochee (MT/yr)",
       caption=paste0('USGS Site ',mouth_site))

ssc_flux

ggsave(ssc_flux, 
       filename = paste0(wd_root, paste0('/exports/USGS-',mouth_site,'_flux.png')),
       width = 12, height = 8)

# Create rating curve
reg = lm(log10_SSC_flux_MTyr~log10_discharge_m3s, data=ssc_q)

# Plot regression

reg_plot = ggplot(ssc_q, aes(x = log10_discharge_m3s, y=log10_SSC_flux_MTyr)) +
  geom_point(color='green') +
  geom_smooth(method='lm', formula= y~x, color='black') +
  annotate(geom='text',label = lm_eqn(reg), parse = TRUE, x = -Inf, y = Inf, hjust = -0.2, vjust = 2) +
  theme_bw() +
  scale_fill_manual(values = c('gray'), name = "Metrics")  +
  labs(title=paste0('Rating Curve for Station USGS-',mouth_site),
       caption=paste0(startDate,' to ', endDate))

ggsave(reg_plot, 
       filename = paste0(wd_root, paste0('/exports/USGS-',mouth_site,'.png')),
       width = 10, height = 8)

# Apply regression to discharge data
mouth_q$log10_discharge_m3s <- log10(mouth_q$flow_m3s)

ssc_flux = predict.lm(reg, newdata=mouth_q)
mouth_q$log10_SSC_flux_MTyr <- ssc_flux
mouth_q$SSC_flux_MTyr <- 10**ssc_flux
mouth_q$SSC_mgL <- (10**ssc_flux) / (mouth_q$flow_m3s * 3.10585 * 10**-5)
mouth_q$log10_SSC_mgL <- log10((10**ssc_flux) / (mouth_q$flow_m3s * 3.10585 * 10**-5))

pred <- mouth_q
# Save predicted data
write.csv(pred, paste0(wd_root,"/exports/", mouth_site,"_ssc_pred.csv"), row.names=FALSE)

# Plot SSC flux over time
ssc_flux_plot <- ggplot(pred, aes(x=year_chunk, y=SSC_flux_MTyr)) +
  # geom_point() +
  stat_summary(geom = 'line', fun = 'mean', group=1, aes(color="Average SSC Flux (MT/yr)")) +
  stat_summary(geom = 'errorbar', aes(color='1 standard Error'), fun.data= mean_se,
               fun.args = list(mult = 1), # mult = # of standard errors
               size = 0.5,
               width =  0.2,
               show.legend=TRUE) +
  coord_cartesian(ylim=c(0,1.2)) +
  scale_color_manual(values = c("green", "red")) +
  season_facet +
  labs(title="Rating Curve Derived SSC\nFlux at the Mouth of \nthe Chattahoochee (MT/yr)",
       caption=paste0('USGS Site ',mouth_site))

ssc_flux_plot

ggsave(ssc_flux_plot, 
       filename = paste0(wd_root, paste0('/exports/USGS-',mouth_site,'_rating_flux.png')),
       width = 12, height = 8)

# Plot discharge over time
# Got annual flow from https://waterdata.usgs.gov/nwis/annual?referred_module=sw&amp;site_no=02359170&amp;por_02359170_26942=2396790,00060,26942,1977,2022&amp;start_dt=1984&amp;end_dt=2022&amp;year_type=W&amp;format=html_table&amp;date_format=YYYY-MM-DD&amp;rdb_compression=file&amp;submitted_form=parameter_selection_list
annual_q <- data.table(year=seq(1984,2021), flow_ft3s=c(
  31460,
  16070,
  19050,
  25600,
  16380,
  19270,
  29040,
  26200,
  21590,
  28180,
  30900,
  26820,
  26300,
  24250,
  36860,
  18020,
  10990,
  16890,
  10560,
  28960,
  18170,
  35230,
  16330,
  12420,
  14010,
  23590,
  32160,
  12100,
  9715,
  22340,
  25360,
  18680,
  28020,
  19050,
  30210,
  32090,
  29210
))
annual_q$flow_m3s <- annual_q$flow_ft3s * 0.02832

discharge_plot<- ggplot(annual_q, aes(x=year, y=flow_m3s)) +
  stat_summary(geom = 'line', fun = 'mean', group=1) +
  season_facet +
  coord_cartesian(ylim=c(0,1100)) +
  labs(title="Average Discharge at the Mouth of the Chattahoochee (m3/s)",
       x="year") +
  stat_summary(aes(label=round(..y..,0)), fun='mean', geom="text", size=2,
             vjust = -1) 

ggsave(discharge_plot, 
       filename = paste0(wd_root, paste0('/exports/USGS-',mouth_site,'_discharge.png')),
       width = 20, height = 8)

```

## Investigate SSC FLux along the whole river transect

```{r}
# Import transect topography
transect_topo <- read.csv("D:\\valencig\\Thesis\\Data\\chattahoochee_landsat\\chattahoochee_transect_topo.csv")
# Cant convert to km2 because cell size varies with latitude
transect_topo <- data.frame(
  distance_km = as.numeric(transect_topo$distance_km),
  elev_min = as.numeric(transect_topo$elev_min),
  flow_acc_max= as.numeric(transect_topo$flow_acc_max) 
  
)

# Need to convert  flow ft^3/2 to m^3/2
Q_full_mc$flow_m3s <- Q_full_mc$flow * 0.02832

# Convert distance downstream to nearest 2 km to match with landsat data
Q_full_mc$dist_downstream_2km <- round(Q_full_mc$dist_downstream_km/2)*2

# ggplot(Q_full_mc, aes(x=dist_downstream_km, y=flow_m3s)) +
#   stat_summary(geom='line', fun='mean', na.rm=T) +
#   facet_wrap(~year_chunk)

# Merge flow data with landsat data
# landsat_flux <- landsat_data_filter %>% dplyr::select(-c(lat, lon))
landsat_flux <- left_join(landsat_data_filter, 
                          subset(Q_full_mc, select=c(date, dist_downstream_2km, flow_m3s)), 
                          by=c('date', 'distance_km'='dist_downstream_2km'))
# Merge topographic data with landat data
landsat_flux <- left_join(landsat_flux, transect_topo, by="distance_km")
# Set identifier for distances with flux
landsat_flux$in_situ_flow <- F
landsat_flux[!is.na(flow_m3s),]$in_situ_flow <- T
landsat_flux$flow_m3s_log10 <- log10(landsat_flux$flow_m3s)
landsat_flux$flow_acc_log10 <- log10(landsat_flux$flow_acc_max)

# Create folder to hold regression plots
wd_continuous_Q <- paste0(wd_root, '/exports/continuous_Q_reg/')
if(!dir.exists(wd_continuous_Q)){
    dir.create(wd_continuous_Q)
}

# Fill in Q_full_mc data
Q_full_mc$flow_m3s_log10 <- log10(Q_full_mc$flow_m3s)
names(Q_full_mc)[names(Q_full_mc) == "dist_downstream_2km"] <- "distance_km"
Q_full_mc <- left_join(Q_full_mc, transect_topo, by=("distance_km"))
Q_full_mc$flow_acc_log10 <- log10(as.numeric(Q_full_mc$flow_acc_max))
# Remove NaN values created from log10
Q_full_mc <- Q_full_mc %>% filter(is.finite(flow_m3s_log10))

# Baseline Attempt --> create discharge vs. drainage curve every day
naive_reg <- function(.x){
  # in_situ_flow <- .x %>% filter(in_situ_flow == T)
  # Case 1: no in-situ flow measurements at that day
  # Issue: around 700 of 1650 dates of landsat sample do not have in-situ flow information
  # if (nrow(in_situ_flow) == 0) {
  #   .x$added_flow = F
  #   return(.x)
  # }
  in_situ_flow <- Q_full_mc %>% filter(date==.x$date2[1])
  # Case 2: There are flow measurements, perform linear regression
  reg <- lm(flow_m3s_log10~flow_acc_log10, data = in_situ_flow)
  eq <- substitute(italic('Flow_m3s') == 10^a %.%italic('Hydroshed_pixels')^b, 
         list(a = format(unname(coef(reg)[1]), digits = 3),
              b = format(unname(coef(reg)[2]), digits = 3)))
    
  reg_plot = ggplot(in_situ_flow, aes(x=flow_acc_log10, y=flow_m3s_log10)) +
    geom_point() +
    geom_smooth(method = "lm", se=FALSE, color="green", formula = y ~ x) +
    annotate(geom='text', label = as.character(as.expression(eq)), 
             parse = T, x = -Inf, y = Inf, hjust = 0, vjust = 1) +
    season_facet +
    labs(title=paste0('Date', .x$date2[1]),
        x='Drainage Area (log10 Hydroshed pixels)',
        y='Discharge (log10 m3s)')
  
  # Save regression plot
  ggsave(reg_plot, 
       filename = paste(wd_continuous_Q, .x$date2[1], '.pdf'),
       width = 8, height = 8)
  .x[.x$in_situ_flow == F, ]$flow_m3s_log10 <- predict(reg, .x[.x$in_situ_flow == F,])
  .x[.x$in_situ_flow == F, ]$flow_m3s <- 10**.x[.x$in_situ_flow == F,]$flow_m3s_log10
  return(.x)
}

# Add dummy date to access date inside of group modify
landsat_flux$date2 <- landsat_flux$date

landsat_flux <- landsat_flux %>%
  group_by(date) %>%
  group_modify(~naive_reg(.)) %>% 
  subset(select=-c(date2))
# %>% 
#   filter(flow_m3s_predict>=0)

ggplot(landsat_flux, aes(x=distance_km, y=flow_m3s)) +
  # geom_point() + 
  stat_summary(fun='mean', geom="line", aes(color="regressed")) +
  stat_summary(data = Q_full_mc, fun='mean', geom="line", aes(color="in-situ")) +
  season_facet +
  # coord_cartesian(ylim=c(0,750)) +
  labs(title="Comparison of in-situ and regressed discharge")

```

# Continue investigating flux at every point

```{r}
# Determine flux at every point
landsat_flux$SSC_flux_MTyr <- landsat_flux$flow_m3s * landsat_flux$SSC_mgL * 3.10585 * 10**-5

# Reduce and get average for one sample per day
landsat_day_avg <- landsat_flux %>% group_by(distance_km, date) %>% 
  summarise_at(c("SSC_flux_MTyr","flow_m3s","SSC_mgL"), mean) %>%
  left_join(subset(landsat_flux, 
                   select=-c(SSC_flux_MTyr, flow_m3s, SSC_mgL)), by=c("date", "distance_km")) %>%
  distinct()

transect_flux_plot <- ggplot(landsat_day_avg, 
                             aes(x=distance_km, y=SSC_flux_MTyr, color="Landsat Derived\nSSC Flux (MT/yr)")) +
  # geom_point() +
  stat_summary(geom = 'line', fun = 'mean', group=1, aes(color="Average SSC Flux (MT/yr)"), na.rm=T) +
  # stat_summary(geom = 'errorbar', aes(color='1 standard Error'), fun.data= mean_se,
  #              fun.args = list(mult = 1), # mult = # of standard errors
  #              size = 0.5,
  #              width =  0.2,
  #              show.legend=TRUE) +
  # coord_cartesian(ylim=c(0,2)) +
  scale_color_manual(values = c("green")) +
  season_facet +
  facet_wrap(~year_chunk) +
  labs(title="SSC Flux along the Chattahoochee Transect",
       caption="Reduced to one average sample per day per transect section.")

transect_flux_plot

transect_flow_plot <- ggplot(landsat_day_avg, 
                             aes(x=distance_km, y=flow_m3s, color="Flow_m3s")) +
  # geom_point() +
  stat_summary(geom = 'line', fun = 'mean', group=1, na.rm=T) +
  scale_color_manual(values = c("red")) +
  season_facet +
  facet_wrap(~year_chunk) +
  labs(title="Discharge along the Chattahoochee Transect",
       caption="Reduced to one average sample per day per transect section.")

transect_flow_plot

# USGS Station is roughly 10 km upstream, add 2 km buffer
landsat_mouth <- landsat_day_avg %>% 
  filter(distance_km<=max(landsat_day_avg$distance_km)-8 & distance_km>=max(landsat_day_avg$distance_km)-12)

landsat_flux_mouth_plot <- ggplot(landsat_mouth, aes(x=year_chunk, y=SSC_flux_MTyr, color="Landsat Derived\nSSC Flux (MT/yr)")) +
  # geom_point() +
  stat_summary(geom = 'line', fun = 'mean', group=1, aes(color="Landsat Derived\nSSC Flux (MT/yr)")) +
  stat_summary(geom = 'errorbar', aes(color='1 standard Error'), fun.data= mean_se,
               fun.args = list(mult = 1), # mult = # of standard errors
               size = 0.5,
               width =  0.2,
               show.legend=TRUE) +
  # coord_cartesian(ylim=c(0,2)) +
  scale_color_manual(values = c("green", "purple")) +
  season_facet +
  labs(title="SSC Flux at the mouth of the chattahoochee",
       caption="Reduced to one average sample per day.")

landsat_flux_mouth_plot

# Combine with no rating curve in-situ measurements
mouth_flux_compare <- ggplot(landsat_mouth, aes(x=year_chunk, y=SSC_flux_MTyr)) +
  # geom_point() +
  stat_summary(geom = 'line', fun = 'mean', group=1, aes(color="Landsat Derived\nSSC Flux (MT/yr)")) +
  stat_summary(geom = 'errorbar', 
               aes(color='1 standard deviation'), 
               fun.data= mean_sdl,
               fun.args = list(mult = 1), # mult = # of standard errors
               size = 0.5,
               width =  0.2,
               show.legend=TRUE) +
  # geom_point() +
  stat_summary(data=ssc_day_avg, geom = 'line', fun = 'mean', group=1, aes(x=year_chunk, y=SSC_flux_MTyr, color="In-Situ SSC Flux (MT/yr)")) +
  stat_summary(data=ssc_day_avg, 
               geom = 'errorbar', 
               aes(x=year_chunk, y=SSC_flux_MTyr, color='1 standard deviation'), 
               fun.data= mean_sdl,
               fun.args = list(mult = 1), # mult = # of standard errors
               size = 0.5,
               width =  0.2,
               show.legend=TRUE) +
  season_facet +
  coord_cartesian(ylim=c(0, 5)) +
  scale_color_manual(values = c("green", "purple","red")) +
  labs(title="SSC Flux at the mouth of the chattahoochee",
       caption="Reduced to one average sample per day.",
       x="year")

mouth_flux_compare 

# Save plots
ggsave(transect_flux_plot, 
       filename = paste0(wd_root, '/exports/transect_flux.png'),
       width=12, height=8)

ggsave(transect_flow_plot, 
       filename = paste0(wd_root, '/exports/transect_flow.png'),
       width = 12, height = 8)

ggsave(landsat_flux_mouth_plot, 
       filename = paste0(wd_root, '/exports/landsat_mouth_flux.png'),
       width = 12, height = 8)

ggsave(mouth_flux_compare , 
       filename = paste0(wd_root, '/exports/mouth_flux_compare_year_chunk.png'),
       width = 20, height = 8)
```
# Save variables
```{r}
save(Q_full_mc, file=paste0(save_dir, "Q_full_mc.RData"))
save(landsat_data_filter, file=paste0(save_dir, "landsat_data_filter.RData"))
save(landsat_flux, file=paste0(save_dir, "landsat_flux.RData"))
save(landsat_day_avg, file=paste0(save_dir, "landsat_day_avg.RData"))
save(landsat_mouth, file=paste0(save_dir, "landsat_mouth.RData"))
save(ssc_day_avg, file=paste0(save_dir, "ssc_day_avg.RData"))
save(ssc_q, file=paste0(save_dir, "ssc_q.RData"))
```

# Investigate some stats using continuous discharge

Use 'landsat_mouth' and 'ssc_day_avg' to avoid sampling bias

```{r}
t1 <- levels(landsat_flux$year_chunk)[1]
t2 <- levels(landsat_flux$year_chunk)[8]

ylims_landsat <- landsat_mouth %>%
  group_by(year_chunk) %>%
  summarise(Q1 = quantile(SSC_flux_MTyr, 1/4, na.rm=T), Q3 = quantile(SSC_flux_MTyr, 3/4, na.rm=T)) %>%
  ungroup() %>%
  #get lowest Q1 and highest Q3
  summarise(lowQ1 = min(Q1), highQ3 = max(Q3))

ylims_ssc <- ssc_day_avg %>%
  group_by(year_chunk) %>%
  summarise(Q1 = quantile(SSC_flux_MTyr, 1/4, na.rm=T), Q3 = quantile(SSC_flux_MTyr, 3/4, na.rm=T)) %>%
  ungroup() %>%
  #get lowest Q1 and highest Q3
  summarise(lowQ1 = min(Q1), highQ3 = max(Q3))

# Violin Plots 

ggplot(landsat_mouth, aes(x=year_chunk, y=SSC_flux_MTyr)) +
  # coord_cartesian(ylim=c(0,3)) +
  coord_cartesian(ylim = as.numeric(ylims_ssc)*1.05) +
  geom_violin(scale="count", aes(fill = year_chunk)) +
  geom_boxplot(width=0.2, outlier.shape=NA) +
  scale_fill_brewer(palette="Blues") + theme_classic()

ggplot(ssc_day_avg, aes(x=year_chunk, y=SSC_flux_MTyr)) +
  # coord_cartesian(ylim=c(0,3)) +
  coord_cartesian(ylim = as.numeric(ylims_ssc)*1.05) +
  geom_violin(scale="count", aes(fill = year_chunk)) +
  geom_boxplot(width=0.2, outlier.shape=NA) +
  scale_fill_brewer(palette="Blues") + theme_classic()

# Side by side box plot
ggplot(ssc_day_avg, aes(x=year_chunk, y=SSC_flux_MTyr, color="In-Situ")) +
  # coord_cartesian(ylim=c(0,3)) +
  coord_cartesian(ylim = as.numeric(ylims_ssc)*1.05) +
  # geom_violin(scale="count", aes(fill = year_chunk)) +
  geom_boxplot(width=0.2, outlier.shape=NA, position= position_nudge(x=-.13)) +
  geom_boxplot(data=landsat_mouth, aes(color="Landsat"), width=0.2, outlier.shape=NA, position= position_nudge(x=+.13)) +
  # Add labels for amount of observations
  # geom_text(data = landsat_flux, aes(label=count), 
  #           position=position_dodge(width=1.0)) +
  scale_fill_brewer(palette="Blues") + theme_classic() +
  labs(title="")

```

# Initalize data for time series comparison

```{r}

basin_area <- st_area(riverdata$basin) %>% set_units(km^2)

### PRE-ANTHROPOGENIC ###

# From octopusdata.org 
# Octupus ID: S156WTS010 Sample ID: SAP66
Be10E <- 9.15 %>% set_units(mm/kyr) %>% set_units(m/yr)
Be10dE <- 2.15 %>% set_units(mm/kyr) %>% set_units(m/yr)

# Get total flux over one year (using density of quartz, 2.648 g/cm^3)
Be10flux <- (Be10E * set_units(basin_area, m^2) * set_units(2648, kg/m^3)) %>% set_units(Mt/yr)
Be10dflux <- (Be10dE * set_units(basin_area, m^2) * set_units(2648, kg/m^3)) %>% set_units(Mt/yr)

### PRE-DAM ###

# From Trimble (1977), sourced originally from Dole and Stabler (1909)
# They used assumed bulk density of 1440 kg/m^3 
# Included 10% additional to account for Bed Load (B.L/)
Tflux <- ((set_units(0.057, mm/yr) %>% set_units(m/yr)) 
          * set_units(basin_area, m^2) 
          * set_units(1440, kg/m^3)) %>% set_units(Mt/yr)

### POST-DAM ###

#USGS in-situ data (at station closest to mouth - USGS-02359170)
USGSflux <- mean(ssc_day_avg$SSC_flux_MTyr) %>% set_units(Mt/yr)
USGSdflux <- sd(ssc_day_avg$SSC_flux_MTyr) %>% set_units(Mt/yr)
USGSQ <- mean(ssc_day_avg$flow_m3s) %>% set_units(m^3/s)
USGSdQ <- sd(ssc_day_avg$flow_m3s) %>% set_units(m^3/s)
USGSDisYield <- (USGSflux / basin_area) %>% set_units(t/(km^2*yr))
USGSSSC <- mean(ssc_day_avg$sscmg_L) %>% set_units(mg/L)
USGSdSSC <- sd(ssc_day_avg$sscmg_L) %>% set_units(mg/L)

# Landsat Data (use last 10 km of the river)
Landsatflux <- mean(landsat_day_avg[landsat_day_avg$distance_km>=(max(landsat_day_avg$distance_km)-10),]$SSC_flux_MTyr, na.rm=T) %>% set_units(Mt/yr)
Landsatdflux <- sd(landsat_day_avg[landsat_day_avg$distance_km>=(max(landsat_day_avg$distance_km)-10),]$SSC_flux_MTyr, na.rm=T) %>% set_units(Mt/yr)
LandsatQ <- mean(landsat_day_avg[landsat_day_avg$distance_km>=(max(landsat_day_avg$distance_km)-10),]$flow_m3s, na.rm=T) %>% set_units(m^3/s)
LandsatQ <- sd(landsat_day_avg[landsat_day_avg$distance_km>=(max(landsat_day_avg$distance_km)-10),]$flow_m3s, na.rm=T) %>% set_units(m^3/s)
LandsatSSC <- mean(landsat_day_avg[landsat_day_avg$distance_km>=(max(landsat_day_avg$distance_km)-10),]$SSC_mgL, na.rm=T) %>% set_units(mg/L)
LandsatdSSC <- mean(landsat_day_avg[landsat_day_avg$distance_km>=(max(landsat_day_avg$distance_km)-10),]$SSC_mgL, na.rm=T) %>% set_units(mg/L)

# Data from Milliman et. al
MillimanQ <- (set_units(22, km^3/yr)) %>% set_units(m^3/s) # Average discharge
MillimanTDS <- set_units(1.1, Mt/yr) # TDS load
MillimanDisYield <- set_units(0.021*1000, t/(km^2*yr)) # They use basin area of 52,000 km^2 but use 52 as divisor, need to multiply by 1,000
MillimanSSC <- set_units(50, mg/L) # Average SSC concentration

# Flux Dataframe
Timeflux <- data.frame(source=c("Reusser (2015)", "Trimble (1977)", "USGS", "Milliman (2013)", "Dethier (2020)"),
                       flux=c(Be10flux, Tflux, USGSflux, MillimanTDS, Landsatflux),
                       period=c("Pre-Antropogenic", "Pre-Dam", "Post-Dam", "Post-Dam", "Post-Dam"))
Timeflux$period <- factor(Timeflux$period, levels = c("Pre-Antropogenic", "Pre-Dam", "Post-Dam"))
Timeflux$source <- factor(Timeflux$source, levels = Timeflux$source)
```

# Create plots over time periods
```{r}
# Compare flux over three time periods
ggplot(Timeflux, aes(x=source, y=flux, fill=period)) +
  geom_bar(stat="identity", color="black") +
  theme_minimal() +
  scale_fill_manual(values=c('#999999','#E69F00','#9CDB79'))
```